%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{comment}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%


\begin{document}
\setlength{\footskip}{5pt}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Alessandro Monticelli} & Email : \href{mailto:alessandro.monticelli@live.it}{alessandro.monticelli@live.it}\\
  & Mobile : +39 340 053 1380 \\
  & \href{https://www.linkedin.com/in/ale-mont/}{LinkedIn: Alessandro Monticelli} \\
  & \href{https://www.github.com/aleemont1}{GitHub: aleemont1}
\end{tabular*}


%-----------EDUCATION-----------------
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {"Alma Mater Studiorum" - University of Bologna}{Cesena (FC), Italy}
      {Bachelor of Science in Computer Science and Engineering}{Sept. 2021 -- Ongoing}
      \resumeItemListStart
          \resumeItem{Relevant Coursework}{Object-Oriented Programming (Java, C\#), High Performance Computing (OpenMP, Open MPI, CUDA, SIMD), 
          Embedded Systems and Internet of Things (Arduino, ESP32 (rtOS), Raspberry Pi), Systems Integration and Virtualization (Docker, Vagrant, Kubernetes, Active Directory), Telecommunication Networks}
      \resumeItemListEnd
  \begin{comment}
    \resumeSubheading
      {I.T.T. "G. Giorgi"}{Brindisi (BR), Italy}
      {High School Diploma in ICT and Telecommunications}{Sept. 2016 -- Jun. 2021}
  \end{comment}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Aurora Rocketry Team - Unibo}{Forlì(FC), Italy}{Embedded Software Engineer}{April 2024 -- Current}
    \resumeItemListStart
        \resumeItem{Technologies used} {C, C++, LoRa}
        \resumeItem{Description}
        {Student organization of the University of Bologna.
	        I took the technical lead for the embedded system engineering process for the avionics.
	        The aim is to participate in EuRoC'25, the European Rocketry Challenge.}
    \resumeItemListEnd
    \resumeSubheading{SPOT. Digital Made Simple}{Cesena(FC), Italy}{Embedded Software Engineer Intern}{February 2024 -- May 2024}
    \resumeItemListStart
        \resumeItem{Technologies used} {Python, .NET 8.0, NuGet}
        \resumeItem{Completed tasks}
        {Refactoring of an IoT platform to manage smart cinema seats.
          Reversed-engineered the driver of the RF module, extracting low-level commands for the control units.
          Engineered a full-fledged simulator of the system to create scenarios and integrations.}
    \resumeItemListEnd
    \resumeSubheading{UBM - Unibo Motorsport Team}{Bologna(BO), Italy}{IT department - Software developer}{October 2023 -- April 2024}
    \resumeItemListStart
        \resumeItem{Technologies used} {Python, Vue.js, MySQL}
        \resumeItem{Completed tasks}
        {Implemented connection pooling for the database, enhancing connections stability and performance. Enhanced the QR code scanning for product placement in warehouses.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\begin{comment}    
    \resumeSubheading
      {UBM - Unibo Motorsport Team}{Bologna, Italy}
      {Software developer}{Oct. 2023 - Current}
      \resumeItemListStart
        \resumeItem{Python}
          {I improved the back-end of the application, implementing new features, 
            documenting the code and fixing bugs.
            In particular:}
            \resumeItemListStart
                \resumeItem{Connection pooling}
                    {I implemented a connection pool to the database, to avoid the overhead of creating a new connection every time a request is made.}
            \resumeItemListEnd
      \resumeItemListEnd

  
    \resumeSubheading
      {Other Company}{Location}
      {Position}{From - To}
      \resumeItemListStart
        \resumeItem{Technology you worked with/on}
          {Description}
        \resumeItem{Other technology you worked with/on}
          {Description}
      \resumeItemListEnd

    \resumeSubheading
      {Research Position}{Location}
      {Position}{From - To}
      \resumeItemListStart
        \resumeItem{Technology you worked with/on}
          {Description}
        \resumeItem{Other technology you worked with/on}
          {Description}
      \resumeItemListEnd
\end{comment}

%-----------LANGUAGES-----------------
\begin{comment}
\section{Languages}
    \resumeSubHeadingListStart
    \resumeItem
      {Italian}{Native speaker}
    \resumeItem
      {English}{Level C1}
  \resumeSubHeadingListEnd
\end{comment}

%--------PROGRAMMING SKILLS------------
\section{Skills}
  I am very confident at using linux. I can install and configure both desktop and server instances, along with various services and applications. \

  I am able to deploy, configure and manage an Active Directory domain on both Windows Server and Linux, with the required services and policies, 
  and execute the join between two domains. \

  I have experience with Docker, and I am able to deploy and manage containers and services, connecting them to a network and managing the volumes. \

  I am proficient in programming in Java, C\# (.NET 8.0), C++ , Python, and C, having a good understanding of the Object-Oriented Programming paradigm, 
  along with the SOLID principles and design patterns. \

  I have particular interest for Embedded Systems and IoT, having experience with Arduino, ESP32 and Raspberry Pi. Some of the projects I have worked on are listed below,
  and I am currently working on a flight computer for a rocket with the Aurora Rocketry Team. \

  I can use Git at a basic level and I have basic experience with CI/CD pipelines, using GitHub Actions. \

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/aleemont1/OKINsimulator}{OKIN Simulator}}
      {Full-fledged simulator of a smart cinema hall, based on a real IoT implementation.
       I engineered and developed the simulator from scratch, using different programming patterns and a modular-by-design approach.}
    \resumeSubItem{\href{https://github.com/aleemont1/esiot-23-24-assignment3/}{River Monitoring System}}
      {Development of a River Monitoring System prototype using ESP32 and Arduino UNO.
       I engineered and developed the River Monitoring Subsystem, implementing data acquisition and
       transmission to the MQTT server, using FreeRTOS task scheduling, along with robust connection and error handling.}
    \resumeSubItem{\href{https://github.com/aleemont1/esiot-23-24-assignment2/}{Smart Car Washing}}
      {Development of a Smart Car Washing prototype using Arduino UNO. 
      I led the backend development, engineering the FSM, implementing the scheduler, and designing all the task APIs. 
      Other key contributions include establishing the task dependency system and implementing critical tasks.}
  \resumeSubHeadingListEnd
\end{document}
